letterEditor_revision

### 2023-10-31 manuscript/review/editorsLetter.qmd
update gitignore

I would like to express my sincere gratitude for taking the time to review our manuscript. Your insightful feedback on our findings was immensely helpful.

We have taken all the reviewer\'s comments and suggestions into consideration and have made significant changes to the manuscript. Please find enclosed a detailed report outlining the actions we have taken in response to each of the reviewer's comments.

Thank you again for your time and effort. We look forward to hearing from you soon.

>>>>

Thank you for taking the time to review our manuscript and for your valuable feedback.

In this revised version, we have taken all the reviewer\'s comments and suggestions into consideration and have made significant changes to the manuscript accordingly. We have submitted a detailed report outlining the actions we have taken in response to each of the reviewer's comments. We believe that the changes we have made have significantly improved the quality of our manuscript.

Thank you again for your time. We look forward to hearing from you soon.
